---
title: "Homework 1"
author: Adarsh Ramakrishnan
output: github_document
---

This is my homework 1 solution


Load tidyverse library

```{r libraries}
library(tidyverse)
```


## Problem 1

Creating the specified dataframe

```{r dataframe}
hw1_p1_df = 
  tibble(
    sample_normal = rnorm(10),
    sample_gt0 = sample_normal > 0,
    character_vector = c("h","i","j","k","l","m","n","o","p","q"),
    factor_vector = factor(c("low","mod","high","low","mod","high","low","mod","high","low"))
)
```

Finding mean of each variable in hw1_p1_df

```{r mean}
mean(pull(hw1_p1_df, sample_normal))
mean(pull(hw1_p1_df, sample_gt0))
mean(pull(hw1_p1_df, character_vector))
mean(pull(hw1_p1_df, factor_vector))
```

For the sample_normal, you get an actual mean since they are all numeric.
For the logical vector, all the true and false are converted into 0s and 1s, after which it takes the mean.
Mean isn't calculated for character or factor vectors. 

```{r as_numeric}
as.numeric(pull(hw1_p1_df, sample_normal))
as.numeric(pull(hw1_p1_df, sample_gt0))
as.numeric(pull(hw1_p1_df, character_vector))
as.numeric(pull(hw1_p1_df, factor_vector))
```

The numbers in sample_normal remain as is. 
The logical vector is converted into 0s and 1s as mentioned above
The character vector cannot be converted into numbers
The factor vector is converted into some unintuitive numbers

This explains what happens when you try to take the mean for the logical as you can see the 0 and 1 conversion.
For character vector, there is no way to convert them into numbers and so no way to take the mean.
For the factor vector, there appears to be a way to convert them into numbers. However, the mean function does not return a mean in the previous code chunk. 

```{r vector_conv}
as.numeric(pull(hw1_p1_df, sample_gt0)) * pull(hw1_p1_df, sample_normal)
as.factor(pull(hw1_p1_df, sample_gt0)) * pull(hw1_p1_df, sample_normal)
as.numeric(as.factor(pull(hw1_p1_df, sample_gt0))) * pull(hw1_p1_df, sample_normal)
```


## Problem 2